Analyses

### 2021-10-20 src/analysis/analyses.Rmd
add all source code

```{r "data for analyses",  eval = F}
load(here("data/intermediate/cleaned_experiment.RData"))
source(here("src/analysis/data-for-analyses.R"))
```

@@

## Descriptive Results
```{r "descriptive-results",  eval = F,echo=FALSE, fig.height=15, fig.width=10}
d %>%
  select(POST_2, POST_3, POST_4, ethnic) %>%
  pivot_longer(cols = POST_2:POST_4,
               names_to = "dvs") %>%
  mutate(dvs = recode(dvs,
                      `POST_2` = "DV: Item 2",
                      `POST_3` = "DV: Item 3",
                      `POST_4` = "DV: Item 4"),
         ethnic = if_else(ethnic==0, "Civic Conception", "Ethnic Conception")) %>%
  group_by(ethnic, dvs) %>%
  summarise(means = round(mean(value, na.rm=T),1),
            stdev = sd(value, na.rm=T)) %>%
  mutate(lower = means - (1.56 * stdev),
         upper = means + (1.56 * stdev),
         type = if_else(means <= 5, "below", "above")) %>%
  ggplot(aes(x = ethnic, 
             y =means, label = means,
             ymin = lower, ymax = upper)) +
  geom_point(stat='identity', size=6)  +
  scale_color_manual(values = c("above"=fig_cols[3],
                                "below"=fig_cols[2])) +
  geom_errorbar(width = 0) +
  geom_text(color="white", size=2) +
  facet_grid(dvs~.) +
  labs(y = "0 (negative) - 5 (positive)", 
       x = "", title = "The People as 'Volk' or 'Bürger'?") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position="none",
        legend.title = element_blank(),
        axis.text=element_text(size=8)) +
  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
  coord_flip() 
```

@@

```{r "balance-checks", eval = F, fig.height=10, fig.width=10}
source(here("src/analysis/balance-test.R"))
df
```

```{r "visualize-unbalanced-vars",  eval = F, fig.height=15, fig.width=20}
source(here("src/analysis/distribution_unbalanced_vars.R"))
p1 + p2 + p3 + p4 + plot_layout(ncol=2)
```

@@

## National Identity Hypothesis
```{r "h2a", eval = F, fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2.R"))
p2
```

## Far Right Party ID Hypothesis
```{r "h2b",  eval = F,fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2b.R"))
p3
```

>>>>

```{r "data for analyses"}
load(here("data/intermediate/cleaned_experiment.RData"))
source(here("src/analysis/data-for-analyses.R"))
```

@@

## Descriptive Results
```{r "descriptive-results", echo=FALSE, fig.height=15, fig.width=10}
d %>%
  select(POST_2, POST_3, POST_4, ethnic) %>%
  pivot_longer(cols = POST_2:POST_4,
               names_to = "dvs") %>%
  mutate(dvs = recode(dvs,
                      `POST_2` = "DV: Item 2",
                      `POST_3` = "DV: Item 3",
                      `POST_4` = "DV: Item 4"),
         ethnic = if_else(ethnic==0, "Civic Conception", "Ethnic Conception")) %>%
  group_by(ethnic, dvs) %>%
  summarise(means = round(mean(value, na.rm=T),1),
            stdev = sd(value, na.rm=T)) %>%
  mutate(lower = means - (1.56 * stdev),
         upper = means + (1.56 * stdev),
         type = if_else(means <= 5, "below", "above")) %>%
  ggplot(aes(x = ethnic, 
             y =means, label = means,
             ymin = lower, ymax = upper)) +
  geom_point(stat='identity', size=6)  +
  scale_color_manual(values = c("above"=fig_cols[3],
                                "below"=fig_cols[2])) +
  geom_errorbar(width = 0) +
  geom_text(color="white", size=2) +
  facet_grid(dvs~.) +
  labs(y = "0 (negative) - 5 (positive)", 
       x = "", title = "The People as 'Volk' or 'Bürger'?") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position="none",
        legend.title = element_blank(),
        axis.text=element_text(size=8)) +
  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
  coord_flip() 
```

@@

```{r "balance-checks", fig.height=10, fig.width=10}
source(here("src/analysis/balance-test.R"))
df
```

@@

## National Identity Hypothesis
```{r "h2a", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2a.R"))
p2a
```

## Far Right Party ID Hypothesis
```{r "h2b", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2b.R"))
p2b
```
